A Context Menu for the Real World: Controlling Physical Appliances Through Head-Worn Infrared Targeting

### 2013-10-23 doc/sigchi14/relatedwork.tex
typos
acks, related work

\section{Related Work}
Relevant prior work exists in the areas of remote control of physical appliances, evaluations of pointing in physical space and augmented reality applications. We discuss each in turn.

@@

In several techniques, users select objects of interest with laser pointers. The laser dot provides immediate visual feedback to the user what is being selected (though it does not indicate whether the pointed-at object can indeed be controlled). Furthermore, laser pointer becomes obstrusive when there are other people in the space. Beigl's early AIDA handheld combines laser pointing with IR communication to exchange commands~\cite{beigl_point_1999}. Patel extends this technique by modulating the laser light to communicate the controllers' identity~\cite{patel_2-way_2003} to initiate radio communication. These proofs-of-concept do not include thorough evaluations. Kemp et al. use a laser pointer to indicate to robots which item to pick up in a room~\cite{kemp_point-and-click_2008}.

>>>>

\section{Related Work}
\bjoern{TODO: Add discussion of ~\cite{swindells_that_2002,merrill_augmenting_2007}.}
Relevant prior work exists in the areas of remote control of physical appliances, evaluations of pointing in physical space and augmented reality applications. We discuss each in turn.

@@

In several techniques, users select objects of interest with laser pointers. The laser dot provides immediate visual feedback to the user what is being selected (though it does not indicate whether the pointed-at object can indeed be controlled). Furthermore, laser pointer becomes obtrusive when there are other people in the space. Beigl's early AIDA handheld combines laser pointing with IR communication to exchange commands~\cite{beigl_point_1999}. Patel extends this technique by modulating the laser light to communicate the controllers' identity~\cite{patel_2-way_2003} to initiate radio communication. These proofs-of-concept do not include thorough evaluations. Kemp et al. use a laser pointer to indicate to robots which item to pick up in a room~\cite{kemp_point-and-click_2008}.

### 2013-10-23 doc/sigchi14/sigchi14.tex
acks, related work

\input{introduction}
\input{relatedwork}
\input{interaction}
\input{device}
\input{targeting}
\input{control}
\input{discussion}
\input{conclusion}
\section{Acknowledgments}
This work was partially supported by a Sloan Foundation Fellowship.

>>>>

\input{introduction}
\input{relatedwork}
\input{interaction}
\input{device}
\input{targeting}
\input{control}
\input{discussion}
\input{conclusion}
\section{Acknowledgments}
This work was supported in part by the TerraSwarm Research Center, one of six centers supported by the STARnet phase of the Focus Center Research Program (FCRP) a Semiconductor Research Corporation program sponsored by MARCO and DARPA. Additional support was provided by a Sloan Foundation Fellowship and a Google Research Award.
